|

### 2019-01-17 Paper 2019.Rmd
Powerpoint and some date fixes

In response to criticisms of corruption convictions as a proper measure of corruption, researchers have also developed alternative measures of state level corruption. Boylan and Long make use of surveys of state reporters (2003). Cordis and Milyo deploy the recently available Transactional Records Access Clearinghouse (TRAC) database of political corruption (2016). Dincer and Jonhston introduce a Corruption Reflections Index, which tracks mentions of corruption in Associated Press reports (2016).

A smaller number of scholars have begun connecting these bodies of work to examine the impact of state-level campaign finance regulations on measures of quid pro quo corruption--one of only two questions of import to the Supreme Court as it considers the constitutionality of contribution limits. The exception to this is a 2013 working paper by Cordis and Milyo. In line with Persily and Lammie (2004), Milyo argues that campaign reform efforts have little effect on public perceptions of corruption. This paper seeks to address this gap, putting state level campaign finance data in direct conversation with state level corruption data.

@@

The results for the models examining the relationship between campaign finance limits and the Corruption Reflections Index are less clear. The pair of stars that suggest the presence of individual-to-party limits is associated with a decrease in the Corruption Reflections Index. There is a less than 1% probability that the results are due to chance. How could this be, given that (a) the presence of individual-to-party limits has no association with a change the Corruption Convictions Index; (b) none of the other contribution limits are associated with a change in the Corruption Reflections Index; and (c) there is no correlation between the dollar amount of the individual-to-party limit and the Corruption Reflections Index? In practice, this would mean that states with individual-to-party limits also see lower levels of Associated Press reporting on corruption, but that once limits of any kind are imposed, the level of limit does not matter. It would also mean that only individual-to-party limits matter, not individual-to-candidate or PAC-to-candidate limits. Lastly, it would imply that the presence of such limits has an effect on reporting about corruption, but not on corruption convictions.

@@

The legal implications of the second interpretation are clear and material. The Supreme Court presently equates political donations with political speech, meaning that it is protected by the first amendment, but that preventing corruption or its appearance in the political system is so important that first amendment rights can be abridged to ensure it. For the Court, no other justification--including creating a more informed electorate, or stimulating more competitive elections, or equality of financial participation in elections--is an important enough concern that we should limit political speech in the form of campaign donations. If there is no link between campaign contribution limits and corruption,  the Court may conclude that there is no reason to abridge US citizens’ first amendment rights by limiting campaign donations.

@@

The anti-reform/pro-speech interpretation must also more fully take into account the second half of the court’s reasoning for limiting free speech, the “appearance of corruption.” Cordis and Milyo’s working paper on confidence and trust in state government is an important step in that direction, though they acknowledges that “survey measures that relate to opinion on the integrity of democracy are likely to reflect a much more expansive view of ‘corruption’ than what any Court would consider appropriate (2012). Dincer and Johnston’s surveys of state reporters is another step, but is limited by its design: State reporters’ perceptions are just a proxy, not a direct measure, of public perceptions of corruption (2017).

@@

##Appendix X: Descriptions and Descriptive Statistics of Control Variables 
In their 2006 paper "Corruption in America," Glaeser and Saks make use of the following control variables, which we have included here:

>>>>

In response to criticisms of corruption convictions as a proper measure of corruption, researchers have also developed alternative measures of state level corruption. Boylan and Long make use of surveys of state reporters (2003). Cordis and Milyo deploy the recently available Transactional Records Access Clearinghouse (TRAC) database of political corruption (2013). Dincer and Jonhston introduce a Corruption Reflections Index, which tracks mentions of corruption in Associated Press reports (2016).

Fewer scholars have begun connecting these bodies of work to examine the impact of state-level campaign finance regulations on measures of quid pro quo corruption--one of only two questions of import to the Supreme Court as it considers the constitutionality of contribution limits. The exception to this is a 2013 working paper by Cordis and Milyo, which campaign contribution limits have little effect on public perceptions of corruption. This paper seeks to address this gap in research, building on Cordis and Milyo's work putting state level campaign finance data in direct conversation with state level corruption data.

@@

The results for the models examining the relationship between campaign finance limits and the Corruption Reflections Index are less clear. The pair of stars in the fourth model suggest that the presence of individual-to-party limits is associated with a decrease in the Corruption Reflections Index. There is a less than 1% probability that the results are due to chance. How could this be, given that (a) the presence of individual-to-party limits has no association with a change the Corruption Convictions Index; (b) none of the other contribution limits are associated with a change in the Corruption Reflections Index; and (c) there is no correlation between the dollar amount of the individual-to-party limit and the Corruption Reflections Index? In practice, this would mean that states with individual-to-party limits also see lower levels of Associated Press reporting on corruption, but that once limits of any kind are imposed, the level of limit does not matter. It would also mean that only individual-to-party limits matter, not individual-to-candidate or PAC-to-candidate limits. Lastly, it would imply that the presence of such limits has an effect on reporting about corruption, but not on corruption convictions.

@@

The legal implications of this interpretation are clear and material. The Supreme Court presently equates political donations with political speech, meaning that it is protected by the first amendment, but that preventing corruption or its appearance in the political system is so important that first amendment rights can be abridged to ensure it. For the Court, no other justification--including creating a more informed electorate, or stimulating more competitive elections, or equality of financial participation in elections--is an important enough concern that we should limit political speech in the form of campaign donations. If there is no link between campaign contribution limits and corruption,  the Court may conclude that there is no reason to abridge US citizens’ first amendment rights by limiting campaign donations.

@@

The anti-reform/pro-speech interpretation must also more fully take into account the second half of the court’s reasoning for limiting free speech, the “appearance of corruption.” Primo and Milyo 2006 on confidence and trust in state government is an important step in that direction, though they acknowledges that “survey measures that relate to opinion on the integrity of democracy are likely to reflect a much more expansive view of ‘corruption’ than what any Court would consider appropriate (2006). Dincer and Johnston’s surveys of state reporters is another step, but is limited by its design: State reporters’ perceptions are just a proxy, not a direct measure, of public perceptions of corruption (2017).

@@

##Appendix X: Descriptions and Descriptive Statistics of Control Variables 
In their 2012 paper "Enforcement and Public Corruption: Evidence from the American States," Glaeser and Saks make use of the following control variables, which we have included here:
